\documentclass[10pt]{article}

% ---------- Document Identity (update these only) ----------
\newcommand{\DocStage}{}
\newcommand{\DocTitle}{Your Road to Tier One SOF}
\newcommand{\ProgramName}{182-Week Civilian-to-Selection Readiness Pipeline}
\newcommand{\ProgramSubtitle}{}

% ---------- Page ----------
\usepackage[legalpaper,left=0.5in,right=0.5in,top=0.6in,bottom=0.45in]{geometry}

% ---------- Typography ----------
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{libertinus}
\usepackage{microtype}
\usepackage{parskip}
\usepackage{ragged2e}
\usepackage{textcomp}
\AtBeginDocument{\color{black}}
\AtBeginDocument{\pagecolor{white}}
\AtBeginDocument{\justifying}

% ---------- Landscape pages ----------
\usepackage{pdflscape}

% ---------- Color ----------
\usepackage[table]{xcolor}
\definecolor{StageBlue}{HTML}{1F4E79}
\definecolor{StageBlueDark}{HTML}{163A5A}
\definecolor{LightGray}{HTML}{F2F4F7}
\definecolor{MidGray}{HTML}{D9DEE5}
\definecolor{RuleGray}{HTML}{C7CED8}
\definecolor{HeaderInk}{HTML}{000000}
\definecolor{Ink}{HTML}{000000}

% ---------- Utility ----------
\usepackage{enumitem}
\sloppy
\setlength{\emergencystretch}{2em}

% ---------- Boxes / UI ----------
\usepackage[most]{tcolorbox}

\tcbset{
  charterTitle/.style={
    enhanced,
    colback=StageBlue!4,
    colframe=StageBlue,
    boxrule=1.25pt,
    arc=3pt,
    left=16pt,right=16pt,top=14pt,bottom=14pt,
    borderline north={3.2pt}{0pt}{StageBlue},
    borderline west={4pt}{0pt}{StageBlue},
    borderline south={1.25pt}{0pt}{StageBlue},
    drop shadow={black!25!white},
  },
  charterRule/.style={
    enhanced,
    colback=LightGray,
    colframe=RuleGray,
    boxrule=0.85pt,
    arc=3pt,
    left=12pt,right=12pt,top=10pt,bottom=10pt,
    borderline west={3pt}{0pt}{StageBlue},
  },
  charterBadge/.style={
    enhanced,
    colback=StageBlue,
    coltext=white,
    colframe=StageBlueDark,
    boxrule=0.6pt,
    arc=2pt,
    left=6pt,right=6pt,top=3pt,bottom=3pt,
  }
}
\newtcbox{\Badge}{nobeforeafter,charterBadge}

% ---------- Lists ----------
\setlist[itemize]{leftmargin=1.5em, itemsep=0.25em, topsep=0.25em}
\setlist[enumerate]{leftmargin=1.8em, itemsep=0.25em, topsep=0.25em}

% ---------- TOC ----------
\usepackage{tocloft}
\setcounter{tocdepth}{3}
\setlength{\cftbeforesecskip}{3pt}
\setlength{\cftbeforesubsecskip}{2pt}
\setlength{\cftbeforesubsubsecskip}{0pt}
\renewcommand{\cftsecfont}{\bfseries}
\renewcommand{\cftsecpagefont}{\bfseries}
\renewcommand{\cftsubsecfont}{\normalfont}
\renewcommand{\cftsubsecpagefont}{\normalfont}
\renewcommand{\cftsubsubsecfont}{\normalfont}
\renewcommand{\cftsubsubsecpagefont}{\normalfont}
\setlength{\cftsecindent}{0pt}
\setlength{\cftsubsecindent}{1.25em}
\setlength{\cftsubsubsecindent}{2.8em}
\setlength{\cftsecnumwidth}{2.1em}
\setlength{\cftsubsecnumwidth}{2.8em}
\setlength{\cftsubsubsecnumwidth}{3.6em}

% Remove the built-in TOC heading so only the custom heading is shown
\makeatletter
\renewcommand{\tableofcontents}{\@starttoc{toc}}
\makeatother

% ---------- Header/Footer: page number only ----------
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\fancyfoot[C]{\thepage}

% ---------- Section formatting ----------
\usepackage{titlesec}

\titleformat{\section}
  {\Large\bfseries\color{Ink}}
  {\thesection}{0.6em}{}
  [\vspace{0.25em}\textcolor{StageBlue}{\rule{\linewidth}{0.8pt}}]

\titleformat{\subsection}
  {\large\bfseries\color{Ink}}
  {\thesubsection}{0.6em}{}

\titleformat{\subsubsection}
  {\normalsize\bfseries\color{Ink}}
  {\thesubsubsection}{0.6em}{}

\titlespacing*{\section}{0pt}{0.95em}{0.35em}
\titlespacing*{\subsection}{0pt}{0.65em}{0.25em}
\titlespacing*{\subsubsection}{0pt}{0.55em}{0.2em}

% ---------- Table engine ----------
\usepackage{tabularray}
\UseTblrLibrary{booktabs}

% ---------- tabularray: GLOBAL table treatment ----------
\SetTblrInner{
  cells = {fg=black, bg=white, valign=t},
}

% ---------- Header helpers ----------
\newcommand{\Hdr}[1]{\shortstack[c]{\strut #1\strut}}

% ---------- Lines ----------
\newcommand{\TitleLine}{\textcolor{StageBlue}{\rule{0.98\linewidth}{0.95pt}}}
\newcommand{\SubTitleLine}{\textcolor{RuleGray}{\rule{0.98\linewidth}{0.65pt}}}

% ---------- Continued on next page ----------
\newcommand{\ContinuedOnNextPageInline}{%
  \par
  \vfill
  \noindent\textcolor{RuleGray}{\rule{\linewidth}{1pt}}\vspace{-2pt}
  \noindent\hfill\textit{Continued on next page}\par\vspace{-10pt}
  \noindent\textcolor{RuleGray}{\rule{\linewidth}{1pt}}
  \clearpage
}

% ---------- PDF hyperlinks ----------
\usepackage[hidelinks]{hyperref}
\hypersetup{
  colorlinks=false,
  pdfborder={0 0 0},
  linktoc=all,
  pdftitle={\DocTitle},
  pdfauthor={\ProgramName}
}

% =========================================================
\begin{document}

\section*{6.A — Category and Tier Definitions}
\phantomsection
\addcontentsline{toc}{section}{6.A — Category and Tier Definitions}

\subsection*{6.A.1 Categories}
\phantomsection
\addcontentsline{toc}{subsection}{6.A.1 Categories}

\begin{itemize}
\item 7.01 Strength and Resistance Training Equipment\\
Covers resistance-based capability needed to execute strength and muscular development safely and reproducibly. Includes space-stable resistance options and safe load-handling posture without assuming gym access.

\item 7.02 Hormonal Support and Adaptogens — OTC Education Only\\
Education-only category covering boundaries, contraindication awareness, and clinician referral triggers. It is never a required capability and is not used to justify phase advancement or evidence claims.

\item 7.03 Foundational Health Supplements — OTC\\
Optional OTC support category for baseline nutritional gaps under conservative posture. It must not become a prerequisite for training or gate decisions and must not introduce medical claims.

\item 7.04 Performance and Auxiliary Supplements — OTC\\
Optional OTC category for performance-adjacent supports under conservative governance. It must not be used to mask risk signals or to change test conditions without documentation.

\item 7.05 Cognitive Performance and Energy Enhancers — OTC\\
Optional OTC category that can influence perceived readiness and test comparability. Stability and documentation are required if used; novelty near gates is a validity risk.

\item 7.06 Recovery, Sleep, and Stress-Support Aids — OTC\\
Optional OTC category to support recovery hygiene under conservative posture. It must not replace sleep opportunity, downshift posture, or safety constraints.

\item 7.07 Load-Bearing, Rucking, and Carry Systems\\
Covers load carriage capability required for ruck and carry exposures, including fit/adjustment, load stability, and reproducible configuration. It is a high-consequence category tied to foot/skin durability and safety constraints.

\item 7.08 Conditioning, Endurance, and Aerobic Training Tools\\
Covers tools that enable year-round low-impact conditioning continuity and controllable Cardio modalities. It supports indoor substitution when weather or safety prevents outdoor exposure.

\item 7.09 Health Monitoring, Diagnostics, and Biometrics\\
Covers non-diagnostic monitoring tools used to improve logging fidelity and trend visibility. It is supportive and must not be treated as medical diagnosis or a mandatory gate requirement unless explicitly made so downstream.

\item 7.10 Logistics, Maintenance, Storage, and Sustainment Equipment\\
Covers sustainment systems that prevent predictable execution failure: storage, drying, maintenance, and organization. It reduces friction that causes missed sessions or degraded equipment safety.

\item 7.11 Footwear Systems and Foot Care\\
Covers footwear interface stability, sock systems, blister prevention, and foot maintenance capability. It is a primary constraint for safe locomotion and load carriage progression.

\item 7.12 Recovery, Mobility, and Tissue-Care Implements\\
Covers mobility and tissue-care capability used to reduce stiffness, manage hotspots, and preserve movement quality. It supports durability controls without implying medical treatment.

\item 7.13 Nutrition Preparation and Hydration Systems\\
Covers hydration access and basic preparation capability that supports safe training and consistent execution. It is constrained to non-medical posture and does not prescribe diet programming here.

\item 7.14 Environmental Apparel — Cold, Hot, Wet, Inclement Weather\\
Covers protective apparel required to train safely in temperature, wind, precipitation, and low-light constraints. It supports environment governance without creating unsafe exposure expectations.

\item 7.15 General Training and Daily Wear Apparel\\
Covers general clothing and daily wear needs that prevent friction and enable consistent training execution. It is feasibility-supporting and must remain non-branded and non-commercial here.

\item 7.16 Operational Self-Management Systems — Journaling, Planning, Mental Conditioning\\
Covers planning, journaling, and operational self-management systems that support adherence, documentation quality, and reslot discipline. It is a governance-support category, not therapy or diagnosis.

\item 7.17 Aquatic Training and Water Safety Equipment\\
Covers safety and feasibility capability for swim exposures when they become phase-relevant, including verifiable pool context and safety posture. It does not authorize underwater/breath-hold without governance prerequisites.

\item 7.18 Testing, Timing, Measurement, and Course-Setup Tools\\
Covers the tools required to produce valid, comparable evidence: timers, measurement tools, route/pool verification aids, and setup aids. It is essential for admissibility and audit traceability.

\item 7.19 Protective and Assistive Equipment\\
Covers protective and assistive capability needed to reduce predictable injury risk and to support safe execution where required. It includes generic protective supports and safety aids without medical claims.

\item 7.20 Personal Hygiene, Health, and Sanitation Items\\
Covers hygiene and sanitation capability that reduces illness risk and skin/foot breakdown. It supports sustainment and consistent execution under high-frequency training.
\end{itemize}

\subsection*{6.A.2 Tier System}
\phantomsection
\addcontentsline{toc}{subsection}{6.A.2 Tier System}

\begin{itemize}
\item Tier 0 — None / Household Only\\
No dedicated capability beyond typical household environment. Any substitutes must be safe and must not increase risk. Tier 0 is acceptable only when the phase does not require that category for safety or validity.

\item Tier 1 — Essentials\\
Minimum deployable capability required for a phase. Tier 1 means the phase can be executed safely and tests can be produced validly where applicable.

\item Tier 2 — Expanded / Performance\\
Optional upgrades that increase convenience, reduce friction, or improve performance potential. Tier 2 is not required unless a phase explicitly depends on it.

\item Tier 3 — Advanced / Overbuilt\\
Optional overbuilt capability that increases redundancy, durability, or specialized performance. Tier 3 is not required unless a phase explicitly depends on it.
\end{itemize}

Governance rule (locked):

\begin{itemize}
\item Tier 1 equals minimum deployable capability for a phase.
\item Tier 2 and Tier 3 are optional upgrades and are never required unless a phase explicitly depends on them. If a phase depends on a Tier 2 or Tier 3 capability, it becomes functionally Tier 1 for that phase.
\end{itemize}

\clearpage
\begin{landscape}

\subsection*{6.A.3 Category by Tier Reference Table}
\phantomsection
\addcontentsline{toc}{subsection}{6.A.3 Category by Tier Reference Table}

\begingroup
\scriptsize
\setlength{\tabcolsep}{2pt}
\renewcommand{\arraystretch}{1.12}

\begin{longtblr}{
  width=\linewidth,
  rowhead=1,
  colspec = {
    Q[l,wd=0.85in]
    X[l,1.90]
    X[l,1.00]
    X[l,1.20]
    X[l,1.20]
    X[l,1.20]
  },
  hlines,
  vlines,
  cells = {hsep=6pt, vsep=6pt, halign=l, valign=t},
  cell{1-Z}{1-6} = {fg=black},
  row{odd} = {bg=white},
  row{even} = {bg=LightGray},
  row{1} = {bg=StageBlue!15, fg=black, font=\bfseries, halign=l, valign=t},
}
\Hdr{Category\\Stage 7 \textbf{ID}} &
\Hdr{Description} &
\Hdr{Tier 0\\None Household} &
\Hdr{Tier 1\\Essentials Examples} &
\Hdr{Tier 2\\Expanded Examples} &
\Hdr{Tier 3\\Advanced Examples} \\

7.01 &
Resistance capability to execute strength development safely and reproducibly without assuming gym access. &
Bodyweight and household support surfaces &
Adjustable resistance option; stable anchor-free band set; simple pull support surface &
Additional resistance variety; higher stability setup options &
Redundant resistance systems; expanded implement variety; dedicated training space configuration \\

7.02 &
Hormonal support and adaptogens category, education-only governance boundary set. &
N/A — education-only; never required; clinician-led if ever used. &
N/A — education-only; never required; clinician-led if ever used. &
N/A — education-only; never required; clinician-led if ever used. &
N/A — education-only; never required; clinician-led if ever used. \\

7.03 &
Optional OTC foundational supplement posture for baseline support without medical claims. &
None &
Basic OTC foundational set; stable use pattern; documented context &
Expanded OTC foundational options; improved compliance aids &
Redundant options; extended supply posture; travel continuity posture \\

7.04 &
Optional OTC performance-adjacent supports under conservative governance and stability posture. &
None &
Single stable OTC performance support; documented use context &
Expanded OTC support options; improved standardization posture &
Redundant options; extended stability controls and documentation posture \\

7.05 &
Optional OTC cognitive/energy supports with high validity sensitivity; novelty near gates is restricted. &
None &
Single stable OTC stimulant-equivalent posture; logged use timing &
Expanded options with stricter standardization posture &
Redundant options; conservative stability controls across windows \\

7.06 &
Optional OTC recovery/sleep/stress supports that complement, never replace, sleep opportunity and downshift posture. &
None &
Single stable OTC recovery aid posture; documented context &
Expanded recovery aid options; improved sleep hygiene supports &
Redundant aids; extended sustainment posture under travel/stress \\

7.07 &
Load carriage capability for ruck/carry exposures with reproducible configuration and safe fit. &
None &
Adjustable pack system; load containment method; basic load verification method &
Expanded fit options; improved load stability components &
Redundant pack systems; specialized load stabilization options \\

7.08 &
Conditioning tools enabling safe, controllable low-impact Cardio and indoor substitution when needed. &
Outdoor walking only when safe &
Basic indoor low-impact tool access; stable settings/loggable modality &
Additional modalities; improved controllability; redundancy for access loss &
Multiple modalities; dedicated conditioning space and redundancy posture \\

7.09 &
Non-diagnostic monitoring tools supporting trend visibility and logging fidelity. &
None &
Basic wearable or measurement method; stable logging method &
Additional non-diagnostic metrics capture; improved consistency &
Redundant devices; extended data capture and backup posture \\

7.10 &
Sustainment systems reducing friction: storage, drying, maintenance, organization. &
Household storage only &
Basic drying/maintenance posture; storage containers; simple repair/maintenance kit &
Expanded storage; improved drying; organizational redundancy &
Overbuilt sustainment: dedicated drying/storage; redundant maintenance kits \\

7.11 &
Footwear and footcare system for safe locomotion progression and blister prevention. &
None &
Primary supportive footwear; sock system; blister prevention supplies &
Expanded footwear options for conditions; improved footcare toolkit &
Redundant footwear sets; advanced footcare redundancy and sustainment \\

7.12 &
Mobility and tissue-care implements supporting durability and movement quality without medical treatment claims. &
Floor space only &
Basic mobility tool; basic tissue-care implement; safe surface &
Expanded mobility set; improved recovery options &
Redundant recovery tools; dedicated mobility/recovery space posture \\

7.13 &
Hydration and basic nutrition preparation capability supporting safe training execution. &
Household cups only &
Hydration container; basic electrolyte/hydration posture; simple prep capability &
Expanded prep tools; improved carry capacity; travel continuity &
Redundant containers; overbuilt prep system; sustainment posture \\

7.14 &
Environmental apparel supporting safe cold/hot/wet execution and indoor/outdoor feasibility. &
Household clothing only &
Minimum weather-appropriate layers; basic rain/wind protection &
Expanded layering options; improved climate adaptability &
Overbuilt apparel redundancy; specialized condition coverage \\

7.15 &
General training and daily wear apparel supporting friction-free execution and consistency. &
Existing clothing only &
Basic training apparel set; durable daily wear posture &
Expanded apparel options; improved condition matching &
Redundant apparel inventory; extended sustainment posture \\

7.16 &
Planning/journaling/self-management systems supporting adherence, documentation, and reslot discipline. &
None &
Single system-of-record; planner/journal; simple reminders &
Expanded planning toolkit; improved structure and templates &
Overbuilt operational system; redundancy and archival posture \\

7.17 &
Aquatic training and water safety capability for swim readiness when phase-relevant; does not authorize underwater without governance. &
None &
Basic swim safety posture; pool feasibility and verification method &
Expanded aquatic tools; improved safety and logistics posture &
Redundant aquatic capability; advanced safety logistics posture \\

7.18 &
Timing/measurement/course-setup tools required for admissible tests and audit traceability. &
None &
Timer method; scale; tape; route/pool verification posture &
Expanded measurement tools; improved repeatability aids &
Redundant measurement set; overbuilt course-setup capability \\

7.19 &
Protective and assistive capability to reduce predictable injury risk and support safe execution where required. &
None &
Basic protective supports; assistive safety item &
Expanded protective options; improved risk reduction &
Redundant protective inventory; advanced assistive posture \\

7.20 &
Hygiene and sanitation capability preventing illness and skin/foot breakdown under high-frequency training. &
Household hygiene only &
Basic hygiene kit; sanitation supplies; laundry/drying posture &
Expanded hygiene options; improved travel continuity &
Overbuilt sanitation redundancy; extended sustainment and backup posture \\

\end{longtblr}

\endgroup

\end{landscape}
\clearpage

\end{document}