\documentclass[10pt]{article}

% ---------- Document Identity (update these only) ----------
\newcommand{\DocStage}{}
\newcommand{\DocTitle}{Your Road to Tier One \textbf{SOF}}
\newcommand{\ProgramName}{182-Week Civilian-to-Selection Readiness Pipeline}
\newcommand{\ProgramSubtitle}{}

% ---------- Page ----------
\usepackage[legalpaper,left=0.5in,right=0.5in,top=0.6in,bottom=0.45in]{geometry}

% ---------- Typography ----------
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{libertinus}
\usepackage{microtype}
\usepackage{parskip}
\usepackage{ragged2e}
\usepackage{textcomp}
\AtBeginDocument{\color{black}}
\AtBeginDocument{\pagecolor{white}}
\AtBeginDocument{\justifying}

% ---------- Landscape pages ----------
\usepackage{pdflscape}

% ---------- Color ----------
\usepackage[table]{xcolor}
\definecolor{StageBlue}{HTML}{1F4E79}
\definecolor{StageBlueDark}{HTML}{163A5A}
\definecolor{LightGray}{HTML}{F2F4F7}
\definecolor{MidGray}{HTML}{D9DEE5}
\definecolor{RuleGray}{HTML}{C7CED8}
\definecolor{HeaderInk}{HTML}{000000}
\definecolor{Ink}{HTML}{000000}

% ---------- Utility ----------
\usepackage{enumitem}
\sloppy
\setlength{\emergencystretch}{2em}

% ---------- Boxes / UI ----------
\usepackage[most]{tcolorbox}

\tcbset{
  charterTitle/.style={
    enhanced,
    colback=StageBlue!4,
    colframe=StageBlue,
    boxrule=1.25pt,
    arc=3pt,
    left=16pt,right=16pt,top=14pt,bottom=14pt,
    borderline north={3.2pt}{0pt}{StageBlue},
    borderline west={4pt}{0pt}{StageBlue},
    borderline south={1.25pt}{0pt}{StageBlue},
    drop shadow={black!25!white},
  },
  charterRule/.style={
    enhanced,
    colback=LightGray,
    colframe=RuleGray,
    boxrule=0.85pt,
    arc=3pt,
    left=12pt,right=12pt,top=10pt,bottom=10pt,
    borderline west={3pt}{0pt}{StageBlue},
  },
  charterBadge/.style={
    enhanced,
    colback=StageBlue,
    coltext=white,
    colframe=StageBlueDark,
    boxrule=0.6pt,
    arc=2pt,
    left=6pt,right=6pt,top=3pt,bottom=3pt,
  }
}
\newtcbox{\Badge}{nobeforeafter,charterBadge}

% ---------- Lists ----------
\setlist[itemize]{leftmargin=1.5em, itemsep=0.25em, topsep=0.25em}
\setlist[enumerate]{leftmargin=1.8em, itemsep=0.25em, topsep=0.25em}

% ---------- TOC ----------
\usepackage{tocloft}
\setcounter{tocdepth}{3}
\setlength{\cftbeforesecskip}{3pt}
\setlength{\cftbeforesubsecskip}{2pt}
\setlength{\cftbeforesubsubsecskip}{0pt}
\renewcommand{\cftsecfont}{\bfseries}
\renewcommand{\cftsecpagefont}{\bfseries}
\renewcommand{\cftsubsecfont}{\normalfont}
\renewcommand{\cftsubsecpagefont}{\normalfont}
\renewcommand{\cftsubsubsecfont}{\normalfont}
\renewcommand{\cftsubsubsecpagefont}{\normalfont}
\setlength{\cftsecindent}{0pt}
\setlength{\cftsubsecindent}{1.25em}
\setlength{\cftsubsubsecindent}{2.8em}
\setlength{\cftsecnumwidth}{2.1em}
\setlength{\cftsubsecnumwidth}{2.8em}
\setlength{\cftsubsubsecnumwidth}{3.6em}

% Remove the built-in TOC heading so only the custom heading is shown
\makeatletter
\renewcommand{\tableofcontents}{\@starttoc{toc}}
\makeatother

% ---------- Header/Footer: page number only ----------
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\fancyfoot[C]{\thepage}

% ---------- Section formatting ----------
\usepackage{titlesec}

\titleformat{\section}
  {\Large\bfseries\color{Ink}}
  {\thesection}{0.6em}{}
  [\vspace{0.25em}\textcolor{StageBlue}{\rule{\linewidth}{0.8pt}}]

\titleformat{\subsection}
  {\large\bfseries\color{Ink}}
  {\thesubsection}{0.6em}{}

\titleformat{\subsubsection}
  {\normalsize\bfseries\color{Ink}}
  {\thesubsubsection}{0.6em}{}

\titlespacing*{\section}{0pt}{0.95em}{0.35em}
\titlespacing*{\subsection}{0pt}{0.65em}{0.25em}
\titlespacing*{\subsubsection}{0pt}{0.55em}{0.2em}

% ---------- Table engine ----------
\usepackage{tabularray}
\UseTblrLibrary{booktabs}

% ---------- tabularray: GLOBAL table treatment ----------
\SetTblrInner{
  cells = {fg=black, bg=white, valign=t},
}

% ---------- Header helpers ----------
\newcommand{\Hdr}[1]{\shortstack[c]{\strut #1\strut}}

% ---------- Lines ----------
\newcommand{\TitleLine}{\textcolor{StageBlue}{\rule{0.98\linewidth}{0.95pt}}}
\newcommand{\SubTitleLine}{\textcolor{RuleGray}{\rule{0.98\linewidth}{0.65pt}}}

% ---------- Continued on next page ----------
\newcommand{\ContinuedOnNextPageInline}{%
  \par
  \vfill
  \noindent\textcolor{RuleGray}{\rule{\linewidth}{1pt}}\vspace{-2pt}
  \noindent\hfill\textit{Continued on next page}\par\vspace{-10pt}
  \noindent\textcolor{RuleGray}{\rule{\linewidth}{1pt}}
  \clearpage
}

% ---------- PDF hyperlinks ----------
\usepackage[hidelinks]{hyperref}
\hypersetup{
  colorlinks=false,
  pdfborder={0 0 0},
  linktoc=all,
  pdftitle={\DocTitle},
  pdfauthor={\ProgramName}
}

% =========================================================
\begin{document}

\begin{tcolorbox}
\begin{center}
Stage 9 — Final QA, Packaging, and Implementation Guide\\[0.35em]
\textbf{SOF} Physical Development Transformation Program\\[0.25em]
182-Week Civilian-to-Selection Readiness Pipeline\\[0.65em]
\TitleLine
\end{center}
\end{tcolorbox}

\vspace{0.35em}

\section*{Stage 9 — Final QA, Packaging, and Implementation Guide}
\phantomsection
\addcontentsline{toc}{section}{Stage 9 — Final QA, Packaging, and Implementation Guide}

\subsection*{Introduction}
\phantomsection
\addcontentsline{toc}{subsection}{Introduction}

\subsubsection*{1) Purpose}

Stage 9 exists to produce a release-ready Program v1.0 package from Stages 0–8 without altering technical content except cosmetic fixes where meaning is unchanged. Stage 9 is the deployment layer that consolidates doctrine into a canonical PDF binder and provides the operational bundle, QA status reporting, implementation guidance, and deployment checklists required for execution.

Stage 9 includes deliverables 9.A–9.F. Stage 9 outputs focus on packaging integrity, audit-ready QA status reporting, trainee onboarding artifacts, and controlled change/version discipline with explicit linkage to Stage 8 Issue IDs (\textbf{ISS-08}-\#\#\#).

\subsubsection*{2) Scope}

\paragraph*{Inclusions}

\begin{itemize}
\item Packaging artifacts 9.A–9.F (implementation-facing deliverables; produced in this Stage 9 package).
\item QA status reporting using Stage 8 Issue IDs \textbf{ISS-08}-\#\#\#, including:
  \begin{itemize}
  \item stage-level Pass/Fail plus open issues list,
  \item deliverable-level Pass/Fail plus open issues list.
  \end{itemize}
\item Implementation guidance for coach/admin and trainee usage based on the packaged binder + folder bundle.
\item Versioning and change-control artifacts stored at:
  \begin{itemize}
  \item /99\_Change\_Log\_and\_Archive/Versioning/
  
  containing:
  \item \textbf{CHANGE-LOG}
  \item \textbf{PATCH-REGISTER}
  \item \textbf{FREEZE-WINDOWS}
  
  and a binder pointer to that location.
  \end{itemize}
\item Deployment checklists that verify readiness to execute without relying on unstated assumptions.
\end{itemize}

\paragraph*{Exclusions}

\begin{itemize}
\item No new programming.
\item No new tests, thresholds, phase edits, or equipment-category expansions.
\item No quiet upstream fixes beyond cosmetic corrections where meaning is unchanged.
\item No rewriting or reinterpretation of Stage 8 issues; Stage 8 findings are preserved and carried forward.
\end{itemize}

\subsubsection*{3) How to Use}

\paragraph*{Coach/Admin}

\begin{itemize}
\item Navigate the package as two synchronized components:
  \begin{itemize}
  \item canonical read-only PDF binder for doctrine,
  \item companion folder bundle for operational artifacts (templates, logs, tables, checklists).
  \end{itemize}
\item Use QA status sections to determine deployability:
  \begin{itemize}
  \item review stage-level and deliverable-level Pass/Fail,
  \item review Known Issues referencing \textbf{ISS-08}-\#\#\#,
  \item treat unresolved High-severity \textbf{ISS-08}-\#\#\# as deployment blockers unless explicitly approved under controlled risk acceptance posture.
  \end{itemize}
\item Onboard the trainee using Stage 9 deliverables 9.A–9.F as the required execution layer; earlier stages remain coach-facing reference.
\item Apply change control through the locked versioning location:
  \begin{itemize}
  \item record every substantive change via \textbf{CHANGE-LOG} and \textbf{PATCH-REGISTER},
  \item enforce \textbf{FREEZE-WINDOWS} discipline,
  \item re-run Stage 8 crosswalk posture after any substantive patch.
  \end{itemize}
\end{itemize}

\paragraph*{Trainee}

\begin{itemize}
\item Stage 9 is the execution and implementation layer.
\item All Stage 9 deliverables 9.A–9.F are required reading and execution artifacts.
\item The trainee follows Stage 9 checklists and logs; earlier stages are not treated as the day-to-day operating interface unless explicitly directed by coach/admin.
\end{itemize}

\subsubsection*{4) Inputs and Assumptions}

\paragraph*{Inputs}

\begin{itemize}
\item Stages 0–8 are completed and fixed.
\item Stage 8 Issue Log exists and is authoritative; Issue IDs are \textbf{ISS-08}-\#\#\#.
\item Stage 9 produces Program v1.0 as:
  \begin{itemize}
  \item one canonical PDF binder, and
  \item one companion folder bundle containing operational artifacts.
  \end{itemize}
\end{itemize}

\paragraph*{Assumption Ledger only if needed}

\begin{itemize}
\item Distribution control is managed by coach/admin (read-only binder control; controlled updates to operational bundle).
\item Storage location and access discipline exist for:
  \begin{itemize}
  \item the binder,
  \item the folder bundle,
  \item the versioning/archive path /99\_Change\_Log\_and\_Archive/Versioning/.
  \end{itemize}
\end{itemize}

\subsubsection*{5) Interfaces}

\paragraph*{Upstream dependencies}

\begin{itemize}
\item Stage 8 Issue Log and all upstream artifacts Stages 0–8 are inputs and remain fixed.
\item Stage 9 consumes Stage 8’s coherence state, open issues inventory, and corrective principles as references without modification.
\end{itemize}

\paragraph*{Downstream consumers}

\begin{itemize}
\item Real-world execution and deployment (coach/admin and trainee).
\item Future versioning and patch cycles, including revalidation against Stage 8 crosswalk posture.
\end{itemize}

\paragraph*{Crosswalk hooks}

\begin{itemize}
\item Issue IDs: \textbf{ISS-08}-\#\#\# used consistently across:
  \begin{itemize}
  \item central \textbf{ISSUE-LOG} file,
  \item per-deliverable Known Issues sections,
  \item QA status reporting.
  \end{itemize}
\item Artifact filenames follow locked convention:
  \begin{itemize}
  \item [StageID]-[DeliverableID]\_[Title]\_\_v-1.0
  \end{itemize}
  with:
  \begin{itemize}
  \item hyphens in IDs,
  \item underscores in titles,
  \item no spaces,
  \item version suffix v-1.0 exactly.
  \end{itemize}
\item Folder paths and pointers:
  \begin{itemize}
  \item explicit binder pointer to /99\_Change\_Log\_and\_Archive/Versioning/.
  \end{itemize}
\item Version headers and distribution pointers embedded in the package so recipients know which artifacts are canonical and how updates are governed.
\end{itemize}

\subsubsection*{6) Gate / Acceptance Criteria}

Stage 9 is complete and deployable when:

\begin{itemize}
\item Program v1.0 includes Stage 9 deliverables 9.A–9.F in the package structure.
\item A canonical read-only PDF binder exists and matches the folder bundle contents by:
  \begin{itemize}
  \item stage/deliverable coverage,
  \item titles and identifiers,
  \item version suffix v-1.0.
  \end{itemize}
\item Artifact index is complete and filenames follow the locked naming convention exactly.
\item QA status is declared in required format:
  \begin{itemize}
  \item stage-level Pass/Fail plus open issues list,
  \item deliverable-level Pass/Fail plus open issues list,
  
  with explicit references to \textbf{ISS-08}-\#\#\#.
  \end{itemize}
\item Central \textbf{ISSUE-LOG} file exists containing the Stage 8 Issue Log, and each Stage 9 deliverable includes a Known Issues section listing only relevant \textbf{ISS-08}-\#\#\# IDs.
\item Versioning folder exists at /99\_Change\_Log\_and\_Archive/Versioning/ containing \textbf{CHANGE-LOG}, \textbf{PATCH-REGISTER}, and \textbf{FREEZE-WINDOWS}, and the binder includes a pointer to that location.
\item No new content is introduced:
  \begin{itemize}
  \item cosmetic corrections only are permitted when meaning is unchanged,
  \item substantive discrepancies are referenced to \textbf{ISS-08}-\#\#\# and carried forward as Known Issues rather than silently fixed.
  \end{itemize}
\end{itemize}

\subsubsection*{7) Common Failure Modes + Controls}

\begin{itemize}
\item Quietly fixing earlier stages → prohibited; cite \textbf{ISS-08}-\#\#\# and carry forward as Known Issues; corrections occur only via controlled patching and revalidation.
\item Missing issue IDs → enforce one central \textbf{ISSUE-LOG} and per-deliverable Known Issues sections listing relevant \textbf{ISS-08}-\#\#\# only.
\item Inconsistent filenames → enforce locked naming convention; reject artifacts with spaces, wrong separators, or wrong version suffix.
\item Unclear trainee access posture → enforce rule: Stage 9 deliverables 9.A–9.F are trainee-required; earlier stages are coach reference.
\item Mid-phase edits without change-log → enforce /99\_Change\_Log\_and\_Archive/Versioning/ discipline with \textbf{CHANGE-LOG}, \textbf{PATCH-REGISTER}, \textbf{FREEZE-WINDOWS}; re-run Stage 8 crosswalk posture after substantive changes.
\item Binder and folder bundle drift → enforce synchronization checks: binder pointer to operational artifacts; artifact index cross-checked against folder contents.
\end{itemize}

\subsubsection*{8) Versioning Notes}

\begin{itemize}
\item Stage 9 defines v1.0 packaging posture and the controlling change-log rules for deployment.
\item Later edits require:
  \begin{itemize}
  \item logged version bump,
  \item patch record entry in \textbf{PATCH-REGISTER},
  \item revalidation against Stage 8 crosswalk posture and updated \textbf{ISSUE-LOG}.
  \end{itemize}
\item Cosmetic corrections are allowed only when meaning is unchanged; substantive fixes require controlled patching and explicit \textbf{ISS-08} handling carried forward as Known Issues until resolved.
\end{itemize}

\end{document}