\documentclass[10pt]{article}

% ---------- Document Identity (update these only) ----------
\newcommand{\DocStage}{}
\newcommand{\DocTitle}{Your Road to Tier One SOF}
\newcommand{\ProgramName}{182-Week Civilian-to-Selection Readiness Pipeline}
\newcommand{\ProgramSubtitle}{}

% ---------- Page ----------
\usepackage[legalpaper,left=0.5in,right=0.5in,top=0.6in,bottom=0.45in]{geometry}

% ---------- Typography ----------
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{libertinus}
\usepackage{microtype}
\usepackage{parskip}
\usepackage{ragged2e}
\usepackage{textcomp}
\AtBeginDocument{\color{black}}
\AtBeginDocument{\pagecolor{white}}
\AtBeginDocument{\justifying}

% ---------- Landscape pages ----------
\usepackage{pdflscape}

% ---------- Color ----------
\usepackage[table]{xcolor}
\definecolor{StageBlue}{HTML}{1F4E79}
\definecolor{StageBlueDark}{HTML}{163A5A}
\definecolor{LightGray}{HTML}{F2F4F7}
\definecolor{MidGray}{HTML}{D9DEE5}
\definecolor{RuleGray}{HTML}{C7CED8}
\definecolor{HeaderInk}{HTML}{000000}
\definecolor{Ink}{HTML}{000000}

% ---------- Utility ----------
\usepackage{enumitem}
\sloppy
\setlength{\emergencystretch}{2em}

% ---------- Boxes / UI ----------
\usepackage[most]{tcolorbox}

\tcbset{
  charterTitle/.style={
    enhanced,
    colback=StageBlue!4,
    colframe=StageBlue,
    boxrule=1.25pt,
    arc=3pt,
    left=16pt,right=16pt,top=14pt,bottom=14pt,
    borderline north={3.2pt}{0pt}{StageBlue},
    borderline west={4pt}{0pt}{StageBlue},
    borderline south={1.25pt}{0pt}{StageBlue},
    drop shadow={black!25!white},
  },
  charterRule/.style={
    enhanced,
    colback=LightGray,
    colframe=RuleGray,
    boxrule=0.85pt,
    arc=3pt,
    left=12pt,right=12pt,top=10pt,bottom=10pt,
    borderline west={3pt}{0pt}{StageBlue},
  },
  charterBadge/.style={
    enhanced,
    colback=StageBlue,
    coltext=white,
    colframe=StageBlueDark,
    boxrule=0.6pt,
    arc=2pt,
    left=6pt,right=6pt,top=3pt,bottom=3pt,
  }
}
\newtcbox{\Badge}{nobeforeafter,charterBadge}

% ---------- Lists ----------
\setlist[itemize]{leftmargin=1.5em, itemsep=0.25em, topsep=0.25em}
\setlist[enumerate]{leftmargin=1.8em, itemsep=0.25em, topsep=0.25em}

% ---------- TOC ----------
\usepackage{tocloft}
\setcounter{tocdepth}{3}
\setlength{\cftbeforesecskip}{3pt}
\setlength{\cftbeforesubsecskip}{2pt}
\setlength{\cftbeforesubsubsecskip}{0pt}
\renewcommand{\cftsecfont}{\bfseries}
\renewcommand{\cftsecpagefont}{\bfseries}
\renewcommand{\cftsubsecfont}{\normalfont}
\renewcommand{\cftsubsecpagefont}{\normalfont}
\renewcommand{\cftsubsubsecfont}{\normalfont}
\renewcommand{\cftsubsubsecpagefont}{\normalfont}
\setlength{\cftsecindent}{0pt}
\setlength{\cftsubsecindent}{1.25em}
\setlength{\cftsubsubsecindent}{2.8em}
\setlength{\cftsecnumwidth}{2.1em}
\setlength{\cftsubsecnumwidth}{2.8em}
\setlength{\cftsubsubsecnumwidth}{3.6em}

% Remove the built-in TOC heading so only the custom heading is shown
\makeatletter
\renewcommand{\tableofcontents}{\@starttoc{toc}}
\makeatother

% ---------- Header/Footer: page number only ----------
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\fancyfoot[C]{\thepage}

% ---------- Section formatting ----------
\usepackage{titlesec}

\titleformat{\section}
  {\Large\bfseries\color{Ink}}
  {\thesection}{0.6em}{}
  [\vspace{0.25em}\textcolor{StageBlue}{\rule{\linewidth}{0.8pt}}]

\titleformat{\subsection}
  {\large\bfseries\color{Ink}}
  {\thesubsection}{0.6em}{}

\titleformat{\subsubsection}
  {\normalsize\bfseries\color{Ink}}
  {\thesubsubsection}{0.6em}{}

\titlespacing*{\section}{0pt}{0.95em}{0.35em}
\titlespacing*{\subsection}{0pt}{0.65em}{0.25em}
\titlespacing*{\subsubsection}{0pt}{0.55em}{0.2em}

% ---------- Table engine ----------
\usepackage{tabularray}
\UseTblrLibrary{booktabs}

% ---------- tabularray: GLOBAL table treatment ----------
\SetTblrInner{
  cells = {fg=black, bg=white, valign=t},
}

% ---------- Header helpers ----------
\newcommand{\Hdr}[1]{\shortstack[c]{\strut #1\strut}}

% ---------- Lines ----------
\newcommand{\TitleLine}{\textcolor{StageBlue}{\rule{0.98\linewidth}{0.95pt}}}
\newcommand{\SubTitleLine}{\textcolor{RuleGray}{\rule{0.98\linewidth}{0.65pt}}}

% ---------- Continued on next page ----------
\newcommand{\ContinuedOnNextPageInline}{%
  \par
  \vfill
  \noindent\textcolor{RuleGray}{\rule{\linewidth}{1pt}}\vspace{-2pt}
  \noindent\hfill\textit{Continued on next page}\par\vspace{-10pt}
  \noindent\textcolor{RuleGray}{\rule{\linewidth}{1pt}}
  \clearpage
}

% ---------- PDF hyperlinks ----------
\usepackage[hidelinks]{hyperref}
\hypersetup{
  colorlinks=false,
  pdfborder={0 0 0},
  linktoc=all,
  pdftitle={\DocTitle},
  pdfauthor={\ProgramName}
}

% =========================================================
\begin{document}

\section*{7.17 — Aquatic Training and Water Safety Equipment}
\phantomsection
\addcontentsline{toc}{section}{7.17 — Aquatic Training and Water Safety Equipment}

\subsection*{7.17.1 Purpose \& Scope}
\phantomsection
\addcontentsline{toc}{subsection}{7.17.1 Purpose \& Scope}

7.17 covers the minimum deployable equipment and safety posture for surface swimming in controlled pool environments, with governance-gated late-phase open-water safety contingencies. It includes kit components that enable consistent pool entry, safe execution, clean/dry workflow, and audit-ready logging of pool identity and conditions.

\subsection*{7.17.2 Governance and Safety Boundaries}
\phantomsection
\addcontentsline{toc}{subsection}{7.17.2 Governance and Safety Boundaries}

\begin{itemize}
\item Underwater/breath-hold is supervised-only and prohibited otherwise:
  \begin{itemize}
  \item Any underwater/breath-hold exposure requires all of the following, with no exceptions:
    \begin{itemize}
    \item certified lifeguard present on deck,
    \item dedicated safety spotter in direct visual contact,
    \item controlled pool environment (no open water),
    \item explicit abort discipline (stop at any distress signal),
    \item if any requirement is missing: underwater is not scheduled, not attempted, and is inadmissible.
    \end{itemize}
  \end{itemize}
\item Abort discipline posture (surface swim):
  \begin{itemize}
  \item abort and exit water for distress, disorientation, panic, dizziness, cramps, nausea, or unusual breathlessness.
  \end{itemize}
\item Pool rule compliance posture:
  \begin{itemize}
  \item follow pool rules; no unsafe behaviors; no “prove it” actions.
  \end{itemize}
\item Open-water is higher risk:
  \begin{itemize}
  \item avoid unless governed; treat as governance-gated; do not treat open-water exposure as required.
  \end{itemize}
\item No technique tools posture:
  \begin{itemize}
  \item exclude fins, paddles, snorkel from this overview to prevent drift into technique/progression tooling.
  \end{itemize}
\end{itemize}

\subsection*{7.17.3 Tier Doctrine — Applied to Aquatic Equipment}
\phantomsection
\addcontentsline{toc}{subsection}{7.17.3 Tier Doctrine — Applied to Aquatic Equipment}

\begin{itemize}
\item Tier 0: no dedicated kit; pool access not assumed; non-aquatic substitutions cross-reference 7.08.
\item Tier 1: minimum viable surface swim capability and safety readiness when aquatics becomes required per Stage 6.
\item Tier 2: expanded reliability and comfort tools that improve repeatability and reduce friction, still surface-only.
\item Tier 3: overbuilt redundancy and open-water safety items, governance-gated and “avoid unless governed.”
\end{itemize}

\subsection*{7.17.4 Selection Criteria \& Fit Checks}
\phantomsection
\addcontentsline{toc}{subsection}{7.17.4 Selection Criteria \& Fit Checks}

\begin{itemize}
\item Goggles:
  \begin{itemize}
  \item seal integrity without painful pressure; stable strap; no recurring leaks.
  \end{itemize}
\item Cap:
  \begin{itemize}
  \item secure fit; does not cause headache; visible color improves lane awareness.
  \end{itemize}
\item Ear protection (if used):
  \begin{itemize}
  \item comfortable; does not block situational awareness; discontinue if irritation occurs.
  \end{itemize}
\item Clean/dry workflow:
  \begin{itemize}
  \item towel and bag posture supports consistent post-session drying to prevent mildew.
  \end{itemize}
\item Risk screening posture:
  \begin{itemize}
  \item do not enter pool when ill, dizzy, unusually breathless, or unable to self-regulate; abort posture is mandatory.
  \end{itemize}
\end{itemize}

\subsection*{7.17.5 Setup, Safety, and Anchoring}
\phantomsection
\addcontentsline{toc}{subsection}{7.17.5 Setup, Safety, and Anchoring}

\begin{itemize}
\item Pool identification posture:
  \begin{itemize}
  \item Pool \textbf{ID} and pool length/unit are logged for any test event or comparable swim exposure.
  \end{itemize}
\item Lane conduct posture:
  \begin{itemize}
  \item follow pool rules; avoid unsafe behaviors; do not hang on lane lines or perform prohibited rest behaviors when standard requires surface-only discipline.
  \end{itemize}
\item Abort posture:
  \begin{itemize}
  \item stop immediately for distress, disorientation, panic, cramps, dizziness, nausea, or unusual breathlessness.
  \end{itemize}
\item Underwater governance posture:
  \begin{itemize}
  \item underwater/breath-hold remains prohibited unless all supervision specifications are met.
  \item no progression instruction is provided; this is governance only.
  \end{itemize}
\end{itemize}

\subsection*{7.17.6 Maintenance, Replacement, and Storage}
\phantomsection
\addcontentsline{toc}{subsection}{7.17.6 Maintenance, Replacement, and Storage}

\begin{itemize}
\item Rinse and dry routine:
  \begin{itemize}
  \item rinse goggles/cap; dry fully; prevent mildew in bags.
  \end{itemize}
\item Anti-fog posture:
  \begin{itemize}
  \item use stable method; avoid switching chemicals near protected windows if sensitivity exists.
  \end{itemize}
\item Replacement cues:
  \begin{itemize}
  \item goggle strap cracks; persistent leaks; cap tears; persistent mildew odor in bag.
  \end{itemize}
\item Storage:
  \begin{itemize}
  \item ventilated drying; do not store damp gear sealed.
  \end{itemize}
\end{itemize}

\subsection*{7.17.7 Substitution Rules — Maintain Intent Without Breaking Safety/Validity}
\phantomsection
\addcontentsline{toc}{subsection}{7.17.7 Substitution Rules — Maintain Intent Without Breaking Safety/Validity}

\begin{itemize}
\item If pool access is unavailable or conditions compromise safety/validity:
  \begin{itemize}
  \item substitute with 7.08 conditioning modality; do not claim swim equivalence for gate evidence.
  \item document substitution and reason posture.
  \end{itemize}
\item Stage 2.E logging/validity posture required:
  \begin{itemize}
  \item Pool \textbf{ID} and conditions notes must be recorded for any swim test/event attempt.
  \item missing Pool \textbf{ID}/conditions notes make the event inadmissible for gate purposes.
  \item if substituted: document modality and why; treat swim evidence as not collected.
  \end{itemize}
\end{itemize}

\begin{landscape}

\subsection*{7.17.8 Phase Integration Map — Required}
\phantomsection
\addcontentsline{toc}{subsection}{7.17.8 Phase Integration Map — Required}

\begingroup
\scriptsize
\setlength{\tabcolsep}{2pt}
\renewcommand{\arraystretch}{1.12}

\begin{longtblr}{
  width=\linewidth,
  rowhead=1,
  colspec = {
    Q[l,wd=1.05in]
    Q[l,wd=1.55in]
    X[l,3.05]
    X[l,3.85]
  },
  hlines,
  vlines,
  cells = {hsep=6pt, vsep=6pt, halign=l, valign=t},
  row{odd} = {bg=white},
  row{even} = {bg=LightGray},
  row{1} = {bg=StageBlue!15, fg=black, font=\bfseries, halign=l, valign=m},
}
\Hdr{Phase} &
\Hdr{Required Tier (from Stage 6)} &
\Hdr{What Changes / Becomes Mandatory} &
\Hdr{Notes} \\
Phase 00 &
T0 &
None &
No pool access assumed. Substitute with 7.08 when needed; no swim equivalence claims. \\
Phase 01 &
T0 &
None &
Maintain substitution posture; no aquatic requirement implied. \\
Phase 02 &
T0 &
None &
Maintain substitution posture; no aquatic requirement implied. \\
Phase 03 &
T0 &
None &
Maintain substitution posture; do not introduce aquatics as “make up” for missed run/ruck work. \\
Phase 04 &
T1 (End) &
Tier 1 surface swim kit required by Phase 04 (End): goggles + cap + clean/dry workflow &
Pool access becomes operationally necessary for swim evidence. Underwater remains prohibited unless supervision specifications are met (not implied here). \\
Phase 05 &
T1 (End) &
Maintain Tier 1; improve repeatability by stabilizing kit and pool routines &
Phase 05 (End): no novelty near protected windows; log pool identity and conditions when evidence matters. \\
Phase 06 &
T2 (End) &
Tier 2 repeatability supports become required by Phase 06 (End): backup goggles + stable anti-fog posture &
Higher consequence phases increase the cost of equipment failure; redundancy reduces compromised windows. \\
Phase 07 &
T2 (End) &
Maintain Tier 2; enforce stability and documentation &
Phase 07 (End): avoid last-minute gear changes near protected windows. \\
Phase 08 &
T2 (End) &
Maintain Tier 2; continued surface-only posture &
Phase 08 (End): do not treat aquatics as a recovery shortcut; it remains a scheduled domain with governance posture. \\
Phase 09 &
T2 (End) &
Maintain Tier 2; repeatability posture remains controlling &
Phase 09 (End): pool access disruptions trigger substitution to 7.08; do not claim swim equivalence. \\
Phase 10 &
T2 (End) &
Maintain Tier 2; underwater remains governance-gated and conditional only &
Phase 10 (End): if underwater is ever present, it is supervised-only with lifeguard + spotter; prohibited otherwise. \\
Phase 11 &
T2 (End) &
Maintain Tier 2; preserve low variance near high-consequence windows &
Phase 11 (End): any illness signs abort swim session; reslot rather than forcing. \\
Phase 12 &
T3 (End) &
Tier 3 redundancy required by Phase 12 (End): full redundant kit; optional open-water safety items are governance-gated &
Open-water items are Tier 3 only and “avoid unless governed.” Underwater remains supervised-only; not implied as required. \\
Phase 13 &
T3 (End) &
Maintain Tier 3; consolidation emphasizes repeatability and strict governance &
Phase 13 (End): no novelty near final protected windows; pool identity and conditions logging remains required for admissibility. \\
\end{longtblr}

\endgroup

7.17.8 Phase Integration Map Notes:

\begin{itemize}
\item If any phase artifact requires 7.17 Tier 1 earlier than Phase 04 (End), requires Stage 8 review.
\item If any artifact implies underwater/breath-hold practice without lifeguard + spotter supervision, requires Stage 8 review.
\end{itemize}

\end{landscape}

\subsection*{7.17.9 Risks, Contraindications, and Red Flags}
\phantomsection
\addcontentsline{toc}{subsection}{7.17.9 Risks, Contraindications, and Red Flags}

\begin{itemize}
\item Drowning risk and panic risk:
  \begin{itemize}
  \item distress, disorientation, panic, dizziness, cramps, nausea → abort immediately and exit water.
  \end{itemize}
\item Slip hazards:
  \begin{itemize}
  \item wet deck surfaces increase fall risk; move conservatively; staged footwear posture cross-references 7.11/7.19 where appropriate.
  \end{itemize}
\item Illness exposure risk:
  \begin{itemize}
  \item do not swim when ill or febrile; reslot and substitute.
  \end{itemize}
\item Underwater governance breach posture:
  \begin{itemize}
  \item any unsupervised underwater/breath-hold attempt is prohibited and treated as a safety violation; \textbf{STOP} \textbf{NOW} posture.
  \end{itemize}
\item Validity/logging posture (Stage 2.E linkage):
  \begin{itemize}
  \item Pool \textbf{ID} and conditions notes are required for swim test/event admissibility; missing fields render evidence inadmissible.
  \end{itemize}
\item Requires Stage 8 review triggers:
  \begin{itemize}
  \item any timing mismatch where aquatics is required earlier than Stage 6 indicates,
  \item any content that introduces breath-hold progression or underwater training instruction,
  \item any content that promotes open-water exposure as routine rather than governance-gated.
  \end{itemize}
\end{itemize}

\end{document}