\documentclass[10pt]{article}

% ---------- Document Identity (update these only) ----------
\newcommand{\DocStage}{}
\newcommand{\DocTitle}{Your Road to Tier One SOF}
\newcommand{\ProgramName}{182-Week Civilian-to-Selection Readiness Pipeline}
\newcommand{\ProgramSubtitle}{}

% ---------- Page ----------
\usepackage[legalpaper,left=0.5in,right=0.5in,top=0.6in,bottom=0.45in]{geometry}

% ---------- Typography ----------
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{libertinus}
\usepackage{microtype}
\usepackage{parskip}
\usepackage{ragged2e}
\usepackage{textcomp}
\AtBeginDocument{\color{black}}
\AtBeginDocument{\pagecolor{white}}
\AtBeginDocument{\justifying}

% ---------- Landscape pages ----------
\usepackage{pdflscape}

% ---------- Color ----------
\usepackage[table]{xcolor}
\definecolor{StageBlue}{HTML}{1F4E79}
\definecolor{StageBlueDark}{HTML}{163A5A}
\definecolor{LightGray}{HTML}{F2F4F7}
\definecolor{MidGray}{HTML}{D9DEE5}
\definecolor{RuleGray}{HTML}{C7CED8}
\definecolor{HeaderInk}{HTML}{000000}
\definecolor{Ink}{HTML}{000000}

% ---------- Utility ----------
\usepackage{enumitem}
\sloppy
\setlength{\emergencystretch}{2em}

% ---------- Boxes / UI ----------
\usepackage[most]{tcolorbox}

\tcbset{
  charterTitle/.style={
    enhanced,
    colback=StageBlue!4,
    colframe=StageBlue,
    boxrule=1.25pt,
    arc=3pt,
    left=16pt,right=16pt,top=14pt,bottom=14pt,
    borderline north={3.2pt}{0pt}{StageBlue},
    borderline west={4pt}{0pt}{StageBlue},
    borderline south={1.25pt}{0pt}{StageBlue},
    drop shadow={black!25!white},
  },
  charterRule/.style={
    enhanced,
    colback=LightGray,
    colframe=RuleGray,
    boxrule=0.85pt,
    arc=3pt,
    left=12pt,right=12pt,top=10pt,bottom=10pt,
    borderline west={3pt}{0pt}{StageBlue},
  },
  charterBadge/.style={
    enhanced,
    colback=StageBlue,
    coltext=white,
    colframe=StageBlueDark,
    boxrule=0.6pt,
    arc=2pt,
    left=6pt,right=6pt,top=3pt,bottom=3pt,
  }
}
\newtcbox{\Badge}{nobeforeafter,charterBadge}

% ---------- Lists ----------
\setlist[itemize]{leftmargin=1.5em, itemsep=0.25em, topsep=0.25em}
\setlist[enumerate]{leftmargin=1.8em, itemsep=0.25em, topsep=0.25em}

% ---------- TOC ----------
\usepackage{tocloft}
\setcounter{tocdepth}{3}
\setlength{\cftbeforesecskip}{3pt}
\setlength{\cftbeforesubsecskip}{2pt}
\setlength{\cftbeforesubsubsecskip}{0pt}
\renewcommand{\cftsecfont}{\bfseries}
\renewcommand{\cftsecpagefont}{\bfseries}
\renewcommand{\cftsubsecfont}{\normalfont}
\renewcommand{\cftsubsecpagefont}{\normalfont}
\renewcommand{\cftsubsubsecfont}{\normalfont}
\renewcommand{\cftsubsubsecpagefont}{\normalfont}
\setlength{\cftsecindent}{0pt}
\setlength{\cftsubsecindent}{1.25em}
\setlength{\cftsubsubsecindent}{2.8em}
\setlength{\cftsecnumwidth}{2.1em}
\setlength{\cftsubsecnumwidth}{2.8em}
\setlength{\cftsubsubsecnumwidth}{3.6em}

% Remove the built-in TOC heading so only the custom heading is shown
\makeatletter
\renewcommand{\tableofcontents}{\@starttoc{toc}}
\makeatother

% ---------- Header/Footer: page number only ----------
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\fancyfoot[C]{\thepage}

% ---------- Section formatting ----------
\usepackage{titlesec}

\titleformat{\section}
  {\Large\bfseries\color{Ink}}
  {\thesection}{0.6em}{}
  [\vspace{0.25em}\textcolor{StageBlue}{\rule{\linewidth}{0.8pt}}]

\titleformat{\subsection}
  {\large\bfseries\color{Ink}}
  {\thesubsection}{0.6em}{}

\titleformat{\subsubsection}
  {\normalsize\bfseries\color{Ink}}
  {\thesubsubsection}{0.6em}{}

\titlespacing*{\section}{0pt}{0.95em}{0.35em}
\titlespacing*{\subsection}{0pt}{0.65em}{0.25em}
\titlespacing*{\subsubsection}{0pt}{0.55em}{0.2em}

% ---------- Table engine ----------
\usepackage{tabularray}
\UseTblrLibrary{booktabs}

% ---------- tabularray: GLOBAL table treatment ----------
\SetTblrInner{
  cells = {fg=black, bg=white, valign=t},
}

% ---------- Header helpers ----------
\newcommand{\Hdr}[1]{\shortstack[c]{\strut #1\strut}}

% ---------- Lines ----------
\newcommand{\TitleLine}{\textcolor{StageBlue}{\rule{0.98\linewidth}{0.95pt}}}
\newcommand{\SubTitleLine}{\textcolor{RuleGray}{\rule{0.98\linewidth}{0.65pt}}}

% ---------- Continued on next page ----------
\newcommand{\ContinuedOnNextPageInline}{%
  \par
  \vfill
  \noindent\textcolor{RuleGray}{\rule{\linewidth}{1pt}}\vspace{-2pt}
  \noindent\hfill\textit{Continued on next page}\par\vspace{-10pt}
  \noindent\textcolor{RuleGray}{\rule{\linewidth}{1pt}}
  \clearpage
}

% ---------- PDF hyperlinks ----------
\usepackage[hidelinks]{hyperref}
\hypersetup{
  colorlinks=false,
  pdfborder={0 0 0},
  linktoc=all,
  pdftitle={\DocTitle},
  pdfauthor={\ProgramName}
}

% =========================================================
\begin{document}

\section*{5.E — Alignment With Test Calendar and Deload Map}
\phantomsection
\addcontentsline{toc}{section}{5.E — Alignment With Test Calendar and Deload Map}

\subsection*{5.E.1 Alignment Cross-Check}
\phantomsection
\addcontentsline{toc}{subsection}{5.E.1 Alignment Cross-Check}

\clearpage
\begin{landscape}

\begingroup
\scriptsize
\setlength{\tabcolsep}{2pt}
\renewcommand{\arraystretch}{1.12}

\begin{longtblr}{
  width=\linewidth,
  rowhead=1,
  colspec = {
    Q[l,wd=0.85in]
    X[l,2.20]
    Q[l,wd=1.25in]
    Q[l,wd=1.35in]
    X[l,2.45]
    Q[l,wd=1.10in]
    X[l,2.85]
  },
  hlines,
  vlines,
  cells = {hsep=6pt, vsep=6pt, halign=l, valign=t},
  cell{1-Z}{1-7} = {fg=black},
  row{1} = {bg=StageBlue!15, fg=black, font=\bfseries, halign=l, valign=t},
  row{odd} = {bg=white},
  row{even} = {bg=LightGray},
}
\Hdr{Phase} &
\Hdr{Declared Work:Deload\\ Pattern Stage 3} &
\Hdr{Mid-Phase\\ Test Window} &
\Hdr{End-Phase\\ Test Window} &
\Hdr{Phase Card Mid and End\\ Tests Referenced IDs} &
\Hdr{Phase Card Test Battery\\ Matches Stage 3\\ Y or N} &
\Hdr{Notes / Conflicts} \\

Phase 00 &
16 weeks; baseline Week 1 is Deload+Test; then 3:1 rhythm with Deload+Test Weeks 4/8/12/16 &
Weeks 4, 8, 12 &
Week 16 &
Stage 4 phase card references mid and end batteries including \textbf{SMB}; \textbf{MOB} bundle items; \textbf{ME-L-STS-30}; \textbf{ME-UP-PU-INC}; \textbf{CAL-PLANK}; \textbf{AER-WALK-30}; \textbf{AER-WALK-015}; \textbf{REC-ADH-WK}; \textbf{BODYCOMP} trend evidence (\textbf{C1} / \textbf{MET-2B-001}; \textbf{C3} \textbf{MET-2B-003}–009) and compliance metrics (\textbf{MET-2B-043}/044/045/046). &
N &
Requires Stage 8 review. Stage 3 Phase 00 calendar uses \textbf{RUN} check-ins \textbf{C8} (\textbf{MET-2B-014}) in protected windows, while Stage 4 Phase 00 explicitly excludes run time trials and instead uses walk-based instruments and mobility/function items. Stage 3 also includes Week 1 (baseline) as Deload+Test; Stage 4 Phase 00 does not treat Week 1 as a protected test window. Stage 4 also includes battery constructs not defined as Stage 2 instruments (mobility and Phase 00-specific walk instruments), which breaks Stage 2-only gate integrity. \\

Phase 01 &
22 weeks default; 24-week variant; 3:1 with protected Deload+Test Weeks 4/8/12/16/20 and end gate at Week 22 (default) or Week 24 (variant) &
Weeks 4, 8, 12, 16, 20 &
Week 22 (default) / Week 24 (variant) &
Phase 5.B Phase 01 card exists; alignment review is required against the produced card. &
N &
Requires Stage 8 review. Stage 3 defines Phase 01 as 22 weeks default with a 24-week variant, while Stage 5 duration rules in this project fix Phase 01 at 24 weeks. Window placement must follow Stage 3 as source of truth; duration doctrine conflict must be resolved in Stage 8. \\

Phase 02 &
12 weeks; 3:1; baseline Week 1 is Deload+Test; protected Deload+Test Weeks 4/8/12 &
Weeks 4, 8 &
Week 12 &
Phase 5.B Phase 02 card exists; alignment review is required against the produced card. &
N &
Alignment pending: Stage 3 windows are defined; Phase 5.B card must reference only Stage 2 instruments and place gate-grade testing only in these protected weeks. \\

Phase 03 &
12 weeks; 3:1; baseline Week 1 is Deload+Test; protected Deload+Test Weeks 4/8/12 &
Weeks 4, 8 &
Week 12 &
Phase 5.B Phase 03 card exists; alignment review is required against the produced card. &
N &
Alignment pending: Phase 5.B must map mid-phase and end-phase gates into Weeks 4/8/12 only and preserve Stage 2 instrument integrity. \\

Phase 04 &
12 weeks; 3:1; baseline Week 1 is Deload+Test; protected Deload+Test Weeks 4/8/12 &
Weeks 4, 8 &
Week 12 &
Phase 5.B Phase 04 card exists; alignment review is required against the produced card. &
N &
Alignment pending: Phase 5.B must stage \textbf{RUN}/\textbf{RUCK} gate constructs inside protected windows without implying build-week gate attempts. \\

Phase 05 &
12 weeks; 3:1; baseline Week 1 is Deload+Test; protected Deload+Test Weeks 4/8/12 &
Weeks 4, 8 &
Week 12 &
Phase 5.B Phase 05 card exists; alignment review is required against the produced card. &
N &
Alignment pending: Phase 5.B must anchor the first high-cost extended \textbf{RUN} gate inside Week 12 protected window and preserve spacing intent across domains. \\

Phase 06 &
12 weeks; 4:1; baseline Week 1 is Deload+Test; protected Deload+Test Week 5 and Week 10; Transition Week 11; end gate Week 12 Deload+Test &
Weeks 5, 10 &
Week 12 &
Phase 5.B Phase 06 card exists; alignment review is required against the produced card. &
N &
Alignment pending: Phase 5.B must reflect the 4:1 + Transition posture and must not revert to 3:1 placements. \\

Phase 07 &
12 weeks; 4:1; baseline Week 1 is Deload+Test; protected Deload+Test Week 5 and Week 10; Transition Week 11; end gate Week 12 Deload+Test &
Weeks 5, 10 &
Week 12 &
Phase 5.B Phase 07 card exists; alignment review is required against the produced card. &
N &
Alignment pending: Phase 5.B must preserve 4:1 spacing intent and avoid stacking high-cost domains inside a single protected week. \\

Phase 08 &
12 weeks; 4:1; baseline Week 1 is Deload+Test; protected Deload+Test Week 5 and Week 10; Transition Week 11; end gate Week 12 Deload+Test &
Weeks 5, 10 &
Week 12 &
Phase 5.B Phase 08 card exists; alignment review is required against the produced card. &
N &
Alignment pending: Phase 5.B must treat long-load milestones as dominant events by intent and reslot rather than compress if spacing cannot be protected. \\

Phase 09 &
12 weeks; 4:1; baseline Week 1 is Deload+Test; protected Deload+Test Week 5 and Week 10; Transition Week 11; end gate Week 12 Deload+Test &
Weeks 5, 10 &
Week 12 &
Phase 5.B Phase 09 card exists; alignment review is required against the produced card. &
N &
Alignment pending: Phase 5.B must preserve taper-aware Transition Week 11 posture and keep \textbf{CAL} battery central without displacing \textbf{RUN}/\textbf{RUCK} safety constraints. \\

Phase 10 &
12 weeks; 4:1; baseline Week 1 is Deload+Test; protected Deload+Test Week 5 and Week 10; Transition Week 11; end gate Week 12 Deload+Test &
Weeks 5, 10 &
Week 12 &
Phase 5.B Phase 10 card exists; alignment review is required against the produced card. &
N &
Alignment pending: Underwater (\textbf{C14} \textbf{MET-2B-025}/026) remains conditional under governance; Phase 5.B must state “not scheduled; inadmissible without governance” when prerequisites cannot be guaranteed. \\

Phase 11 &
12 weeks; 4:1; baseline Week 1 is Deload+Test; protected Deload+Test Week 5 and Week 10; Transition Week 11; end gate Week 12 Deload+Test &
Weeks 5, 10 &
Week 12 &
Phase 5.B Phase 11 card exists; alignment review is required against the produced card. &
N &
Alignment pending: Phase 5.B must preserve recovery sensitivity and avoid “make-up stacking” behavior near end gate. \\

Phase 12 &
12 weeks; mixed pattern with verification block: baseline Week 1 Deload+Test; Week 5 Deload+Test; Weeks 9–10 Deload+Test verification block; Transition Week 11; final gate Week 12 Deload+Test &
Week 5 and Weeks 9–10 (verification block) &
Week 12 &
Phase 5.B Phase 12 card exists; alignment review is required against the produced card. &
N &
Alignment pending: Phase 5.B must explicitly represent the two-week verification block and keep tests staged across both weeks without stacking all domains. \\

Phase 13 &
12 weeks; mixed pattern with targeted retest block: baseline Week 1 Deload+Test; Week 5 Deload+Test; Weeks 9–10 Deload+Test targeted retest block; Transition Week 11; final verification Week 12 Deload+Test &
Week 5 and Weeks 9–10 (targeted retest block) &
Week 12 &
Phase 5.B Phase 13 card exists; alignment review is required against the produced card. &
N &
Alignment pending: Phase 5.B must treat Week 12 as a decisive, minimal-density final verification window and default \textbf{HOLD} (Replication) rather than forcing compromised evidence. \\

\end{longtblr}

\endgroup

\end{landscape}
\clearpage

\subsection*{5.E.2 High-Risk Test Spacing Check}
\phantomsection
\addcontentsline{toc}{subsection}{5.E.2 High-Risk Test Spacing Check}

\begin{itemize}
\item Stage 3 anchors major \textbf{RUN}, \textbf{RUCK}, and \textbf{SWIM} tests to Deload+Test windows (or explicitly defined two-week verification blocks in Phase 12–13). Build/Intensify/Transition weeks do not schedule gate-grade tests.
\item Stage 3 shifts from 3:1 patterns (Phases 02–05) to 4:1 patterns (Phases 06–11), adding a Transition week before end gates to reduce fatigue contamination and protect validity.
\item Phase 12–13 use two-week protected verification blocks (Weeks 9–10) to close replication gaps without stacking multiple maximal domains into a single week.
\item Water governance constraints are encoded in Stage 3: underwater remains conditional and is never scheduled without governance prerequisites; if governance is unavailable, it is not scheduled and is not gate-admissible.
\item Phase 00/Phase 01 remain conservative in Stage 3 window design; however, Phase 00 currently shows a material mismatch between Stage 3 and Stage 4 test constructs, flagged as Requires Stage 8 review.
\item Any variant handling that changes duration (Phase 01 default 22 weeks vs 24-week variant) must be treated as a controlled selection and reconciled against the 182-week identity; mismatches remain Requires Stage 8 review until resolved.
\end{itemize}

\subsection*{5.E.3 Gate Integrity Check}
\phantomsection
\addcontentsline{toc}{subsection}{5.E.3 Gate Integrity Check}

\begin{itemize}
\item Stage 3 provides at least one mid-phase protected Deload+Test window and an end-of-phase Deload+Test exit gate window for every phase Phase 00 through Phase 13.
\item Gate decisions rely on admissible evidence only: \textbf{VALID} tests and admissible sessions per Stage 1.F; \textbf{INVALID} tests provide no gate credit and trigger reslot posture rather than advancement.
\item Stage 3 enforces window discipline: missed or invalid gates reslot to the next protected window; no stacking make-ups to compress timelines.
\item Tier and threshold posture remains Stage 2-defined (\textbf{ENTRY} / \textbf{INTERMEDIATE} / \textbf{SELECTION-READY}); Phase cards must map exit intent to Stage 2 tier posture without inventing new thresholds.
\item Dependency readiness posture must remain consistent with Stage 5.D; unmet dependencies default \textbf{HOLD}, with \textbf{REGRESS}/\textbf{MEDICAL} \textbf{HOLD} reserved for explicit triggers.
\item Detected violations are explicitly tagged “Requires Stage 8 review,” including:
  \begin{itemize}
  \item Phase 00 Stage 3 vs Stage 4 test construct mismatch,
  \item Phase 01 duration doctrine conflict (Stage 3 default 22 weeks vs project-level fixed 24-week rule).
  \end{itemize}
\end{itemize}

\end{document}